Reach OPT MSNA 2021

### 2021-07-04 MSNA_2021_Monitoring_report.Rmd
data cleaning update
update on the dashboard.

# df <- time_check(df, time_limit)
df <- df %>% 
  mutate(time_validity = case_when(interview_duration < flag_time_limit & 
                                     interview_duration > time_limit ~ "Flagged", TRUE ~ time_validity))

###########################################################################################################

@@

df <- df %>% 
  mutate(not_eligible = case_when(is.na(hh_size) ~ "yes",
                                      TRUE ~ "no"))

# remove ineligible surveys
df %<>% filter(consent == "yes" & not_eligible == "no")

########## SAMPLE FRAMES ########################
# 
westbank_sample_df <- read_csv("input/sample/Final_sampling_frame_WestBank_95_9_CS 8_B 15.csv")

@@

westbank_sample_inperson <- westbank_sample_df_summarized %>% 
                          dplyr::select(strata, Sample = num_surveys)
westbank_sample_inperson

@@

westbank_tracking_merged_in_person <- left_join(westbank_sample_inperson, westbank_tracking_inperson, by = "strata") %>% 
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Sample,
      TRUE ~ (Accepted - Sample) * -1
    )
  )
func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
sumrow_in_person <- as.data.frame(lapply(westbank_tracking_merged_in_person, func))
sumrow_in_person
westbank_tracking_merged_in_person <- rbind(westbank_tracking_merged_in_person, sumrow_in_person ) %>%
  mutate_all(
    funs(replace_na(.,0)))
westbank_tracking_merged_in_person
########################################################################################

@@

gaza_sample_inperson <- gaza_sample_df_summarized %>% 
                          dplyr::select(strata, Sample = num_surveys)
gaza_sample_inperson

@@

gaza_tracking_merged_in_person <- left_join(gaza_sample_inperson, gaza_tracking_inperson, by = "strata") %>% 
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Sample,
      TRUE ~ (Accepted - Sample) * -1
    )
  )
func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
gaza_sumrow_in_person <- as.data.frame(lapply(gaza_tracking_merged_in_person, func))
gaza_sumrow_in_person
gaza_tracking_merged_in_person <- rbind(gaza_tracking_merged_in_person, gaza_sumrow_in_person ) %>%
  mutate_all(
    funs(replace_na(.,0)))
gaza_tracking_merged_in_person

@@

EJ_sample_inperson <- ej_summarized_sample %>% 
                          dplyr::select(strata, Sample = num_surveys)
EJ_sample_inperson

@@

EJ_tracking_merged_in_person <- left_join(EJ_sample_inperson, EJ_tracking_inperson, by = "strata") %>% 
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Sample,
      TRUE ~ (Accepted - Sample) * -1
    )
  )
func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
EJ_sumrow_in_person <- as.data.frame(lapply(EJ_tracking_merged_in_person, func))
EJ_sumrow_in_person
EJ_tracking_merged_in_person <- rbind(EJ_tracking_merged_in_person, EJ_sumrow_in_person ) %>%
  mutate_all(
    funs(replace_na(.,0)))
EJ_tracking_merged_in_person

>>>>

df <- time_check(df, time_limit)
df <- df %>% 
  mutate(time_validity = case_when(interview_duration < flag_time_limit & 
                                     interview_duration > time_limit ~ "Flagged", TRUE ~ time_validity))

###########################################################################################################
df$time_validity

@@

df <- df %>% 
  mutate(not_eligible = case_when(is.na(hh_size) ~ "yes",TRUE ~ "no"),
         uuid = `_uuid`,
         X_uuid = uuid)

df$not_eligible

############ add full strata
######NOTE ::: CHANGE THE OSLO AREA TO REFLECT THE TOOL, A, B, C
df <- df %>%
  mutate(across(everything(), as.character)) %>%
  mutate(strata =
           case_when(location == "west_bank" & (oslo_area == "area_a" | oslo_area == "area_b") ~ "Area_AB",
                     location == "west_bank" & oslo_area == "area_c" ~ paste(hh_location_wb, oslo_area, sep = "_"),
                     location == "gaza" ~ hh_location_gaza,
                     location == "ej"~ "East_Jerusalem",
                     TRUE  ~  'H2'))

#### df after the time check
#df_raw <- df
#write.xlsx(df_raw, (file = sprintf("output/df_raw_%s.xlsx", today())))

##########################################################################################
# Deleted interviews column
df <- df %>% 
  mutate(
    deleted = case_when(
      time_validity == "Deleted" | consent == "no" | not_eligible == "yes" ~ "yes",
      TRUE ~ "no"))
df$deleted
########## SAMPLE FRAMES ########################
# 
westbank_sample_df <- read_csv("input/sample/Final_sampling_frame_WestBank_95_9_CS 8_B 15.csv")

@@

westbank_sample_inperson <- westbank_sample_df_summarized %>% 
                          dplyr::select(strata, Max_Surveys = num_surveys)
westbank_sample_inperson

@@

westbank_tracking_merged_in_person <- left_join(westbank_sample_inperson, westbank_tracking_inperson, by = "strata") %>% 
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Max_Surveys,
      TRUE ~ (Accepted - Max_Surveys) * -1
    )
  )
func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
sumrow_in_person <- as.data.frame(lapply(westbank_tracking_merged_in_person, func))
sumrow_in_person
westbank_tracking_merged_in_person <- rbind(westbank_tracking_merged_in_person, sumrow_in_person ) %>%
  mutate_all(funs(replace_na(.,0))) %>% 
  dplyr::mutate(Min_Surveys = round(Max_Surveys*0.85,0))
westbank_tracking_merged_in_person <- westbank_tracking_merged_in_person %>% 
          relocate(c("Min_Surveys"), .before = "Max_Surveys")
########################################################################################

@@

gaza_sample_inperson <- gaza_sample_df_summarized %>% 
                          dplyr::select(strata, Max_Surveys = num_surveys)
gaza_sample_inperson

@@

gaza_tracking_merged_in_person <- left_join(gaza_sample_inperson, gaza_tracking_inperson, by = "strata") %>% 
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Max_Surveys,
      TRUE ~ (Accepted - Max_Surveys) * -1
    )
  )
func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
gaza_sumrow_in_person <- as.data.frame(lapply(gaza_tracking_merged_in_person, func))
gaza_sumrow_in_person
gaza_tracking_merged_in_person <- rbind(gaza_tracking_merged_in_person, gaza_sumrow_in_person ) %>%
  mutate_all(
    funs(replace_na(.,0))) %>% 
dplyr::mutate(Min_Surveys = round(Max_Surveys*0.90,0))
gaza_tracking_merged_in_person <- gaza_tracking_merged_in_person %>% 
          relocate(c("Min_Surveys"), .before = "Max_Surveys")
gaza_tracking_merged_in_person

@@

EJ_sample_inperson <- ej_summarized_sample %>% 
                          dplyr::select(strata, Max_Surveys = num_surveys)
EJ_sample_inperson

@@

EJ_tracking_merged_in_person <- left_join(EJ_sample_inperson, EJ_tracking_inperson, by = "strata") %>% 
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Max_Surveys,
      TRUE ~ (Accepted - Max_Surveys) * -1
    )
  )
func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
EJ_sumrow_in_person <- as.data.frame(lapply(EJ_tracking_merged_in_person, func))
EJ_sumrow_in_person
EJ_tracking_merged_in_person <- rbind(EJ_tracking_merged_in_person, EJ_sumrow_in_person ) %>%
  mutate_all(
    funs(replace_na(.,0))) %>% 
dplyr::mutate(Min_Surveys = round(Max_Surveys*0.85,0))
EJ_tracking_merged_in_person <- EJ_tracking_merged_in_person %>% 
          relocate(c("Min_Surveys"), .before = "Max_Surveys")
EJ_tracking_merged_in_person
